---
name: Amelia E. 
surname: Barber
#position: "Postdoctoral Fellow"
#address: "Leibniz HKI - Jena"
phone: +49 0162 390 5970
www: www.barber.science
email: "amelia.barber@gmail.com"
twitter: "frau_dr_barber"
github: ameliabedelia
# linkedin: barberae
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 009999
output: 
  vitae::moderncv:
    theme: classic
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(lubridate)
library(glue)
library(here)
```

<!-- # tl;dr -->

<!--  * Postdoctoral fellow with wet lab and computational biology experience -->
<!--  * Interested in fungal biology and what makes a pathogen a pathogen -->

# Education

```{r edu}

edu <- read_csv2(here("data", "edu.csv")) %>%
  fill(everything())

detailed_entries(edu,
                 when = date,
                 what = degree,
                 where = location,
                 with = university,
                 why = why,
                 .protect = FALSE)
# tribble(
#   ~ Degree, ~ Year, ~ Institution, ~ Where,
#   "PhD", "2016", "University of Utah", "Salt Lake City, UT", 
#   "BS", "2006", "University of Wisconsin-Madison", "Madison, WI",
# ) %>% 
#   detailed_entries(Degree, Year, Institution, Where)
```

# Experience

```{r experience}
experience <- read_csv2(here("data", "experience_rf.csv")) %>%
  fill(what, with, when) %>% 
  mutate(what = str_to_title(what)) %>% 
  filter(with != "F1000 Prime")

detailed_entries(experience,
    what = what,
    when = when,
    where = where,
    with = with,
    why = why,
    .protect = FALSE
  )

```

\pagebreak

# Research Support & Awards

```{r}
support <- read_csv2(here("data", "research_support.csv"), col_types = "ccccc")
awards <- read_csv2(here("data", "awards.csv"), col_types = "ccccc")

support_awards <- bind_rows(support, awards) %>% 
  arrange(desc(when))

brief_entries(support_awards,
    when = when,
    what = what,
    .protect = FALSE
  )
```

# Publications

```{r}
#pubs <- scholar::get_publications("COgbwJ4AAAAJ") 

publications <- read_csv2(here("data", "publications_2.csv")) %>% 
  mutate(date = lubridate::dmy(date))

publications %>%
  filter(include == TRUE) %>%
  arrange(desc(date)) %>%
  mutate(year = year(date)) %>% 
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal,
    .protect = FALSE
  )
# scholar::get_publications("COgbwJ4AAAAJ") %>%
#   #filter(cites > 30) %>%
#   distinct(title, .keep_all = TRUE) %>%
#   transmute(bibtype = "Article", author = as.character(author),
#             title = as.character(title),
#             journaltitle = as.character(journal), year, key = row_number()) %>%
#   RefManageR::as.BibEntry() %>%
#   RefManageR::WriteBib("barber.bib")

#bibliography_entries("~/Documents/R/cv/data/barber.bib") %>% 
#   arrange(desc(year))

```

# Presentations

```{r}

presentations <- read_csv2(here("data", "presentations.csv")) %>%
    mutate(when = dmy(when),
         year = year(when),
         what = str_c(what_plain, where, sep = ". ")) %>%
    arrange(desc(year))

brief_entries(presentations,
              what = what,
              when = year,
              #where = where,
              with = combine,
              .protect = FALSE)
```

# Supervisory Experience

```{r}
supervisory <- read_csv2(here("data", "supervisory.csv")) %>% 
  arrange(desc(when)) 

brief_entries(supervisory,
              what = name,
              when = when,
              with = position)
```

# Academic Teaching Experience

```{r}
teaching <- supervisory <- read_csv2(here("data", "teaching.csv"))

brief_entries(supervisory,
              what = what,
              when = when,
              with = where)
```

# Institutional Service

```{r}
service <- read_csv2(here("data", "service.csv"))

brief_entries(service,
              what = what,
              when = when,
              with = with)
```

# Outreach

```{r}
outreach <- read_csv2(here("data", "outreach.csv"))

brief_entries(outreach,
              what = what,
              when = when)
```


# References

**Oliver Kurzai**, postdoctoral advisor  
Chair, Institute for Hygiene and Microbiology, University of Würzburg, Würzburg, Germany  
Group Leader, Leibniz Institute for Natural Product Research and Infection Biology – Hans Knöll Institute, 
Jena, Germany  
okurzai@hygiene.uni-wuerzburg.de // +49 931 31-88007

\bigskip

**Gianni Panagiotou**  
Head, Systems Biology and Bioinformatics Unit  
Leibniz Institute for Natural Product Research and Infection Biology – Hans Knöll Institute, 
Jena, Germany  
gianni.panagiotou@leibniz-hki.de // +49 3641 532-1759

\bigskip

**Matthew Mulvey**, doctoral advisor  
Professor, Department of Pathology  
University of Utah, Salt Lake City, UT, USA  
mulvey@path.utah.edu // +1 (801) 581-5967



